\documentclass[twocolumn,10pt]{article}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}
\usepackage{titling}
\usepackage{tcolorbox}
\usepackage{epigraph}

% Customize epigraph
\setlength{\epigraphwidth}{0.95\textwidth} % Adjust epigraph width
\renewcommand{\textflush}{flushleft}     % Align quote to the left
\renewcommand{\sourceflush}{flushright}  % Align author to the right
\renewcommand{\epigraphsize}{\itshape} % Font size and style for quote

\title{An Organizational Model for the UOR Foundation}
\author{The UOR Foundation}
\date{\today}
\begin{document}

\twocolumn[
\maketitle
\begin{center}
\epigraph{Truth is ever to be found in simplicity, and not in the multiplicity and confusion of things.}{--- Isaac Newton}
\end{center}
\vspace{10pt}
]

\section*{What is a WHOLE?}
\subsection*{Great Complexity}
As a whole, the forest is widely recognized as \textit{an ecosystem of great complexity}.
Seen in it's entirety the forest is magnificent, brilliant and full of life and energy.
It is in full support and an active participant in that dance of life and energy.
Spawning new forms of life and energy.
Becoming much more than the day before.

It is not difficult to see any organism or organization, real or imaginary, as an ecosystem of great complexity.
Adding to this complexity,  no matter the size or power of the organism, \underline{the fact} that it's environment not only significantly influences it, but is \underline{responsible} for allowing it's existence.

By accepting that only external factors are responsible for our existence, it is \textbf{our honor} to present to you the guiding principles and vision for the UOR Foundation.
This document defines the WHOLE of what the UOR Foundation is and it's purpose.
It also clearly identifies it's components \& parts, providing the means and ways for the ethical and equal treatment of all it's members as well as the care and feeding of the core UOR concepts and objects.

\subsection*{Identifying The Whole}
As a WHOLE, all objects or organizations go through specific \textit{states} that guide and direct the WHOLE\@.
These ``states'' provide a class of best guesses from an observer the actual or real experience of the WHOLE\@.\footnote{The phenomenon of hindsight is useful here, because quite often it appears that after the death or termination of a object, do we find greater understand of that object.
Beware or be careful not to terminate something only to get a better understanding of it\ldots that is just plain rude.}
We say ``best guesses'' to address that the power of an observer's ability to discern away core truths from false truths is unforgiven.
Meaning, if you are wrong, it will be very difficult to believe.
For example, one can easily believe or convince oneself that what they are about to do will be done safely, effectively, and look really cool!
Only to find himself in the hospital or worse, dead.
When before, everyone clearly saw, without a doubt, that what he is about to do is dangerous and probably should not be attempted\ldots but maybe, just maybe it will work this time.
Then go for it!

We jest here, but want to highlight your power and potential to influence the Foundation as a member.
Working with universal and core truths is what made the UOR Machine a reality.
In doing so, we have been and continue to be deeply challenged mentally, emotionally, physically, and spiritually in studying and working with the UOR\@.
It takes a high dose of humility to approach the vast, powerful knowledge of universality or oneness that quantum proves over and over.

In that humility, the UOR Foundation recognizes the following states as the \textit{Universal Class of Creation} for all objects real or imaginary:
Birth-Creation, Growth, Sustainment, Decay, and Death-Termination.\footnote{The order appears logical to you, but to the computer the order is irrelevant. Each state is independent and any object has the potential to be in any state at any time.}
To be clear, at any moment in time, any object or being, real or imaginary is either in one state or in transition between states in the Universal Class of Creation.

Why all this talk about wholes and states, universal classes, and creation?
Let's take a moment to remember that the external environment is \underline{responsible} for the existence of any unique object or being.
What we are attempting here is to reveal this idea called the UOR Foundation and it's survival is dependent on you.
By clearly identifying that all unique things, ideas, or beings fall under a universal set of states, we hope our idea, shared by few, may become apart of and hopefully accepted by many.
Or just one\ldots you.
We care deeply about the UOR because we believe in it's potential.
And the potential is great.
Forgive us as we start from the top and attempt to slide down the mountain of \textit{great complexity}.

We recognize that universally all objects,  and uniquely the UOR Foundation, operate under a system of universal states that defines it's life cycle.
Critical in understanding this, is that the states do not represent it's components or parts.
This point is so critical, it will be repeated now.
The \textit{state} of the WHOLE does not represent any of it's parts or components.
At best, it is only a guess as to the overall state that the WHOLE is experiencing.

From this high-abstract perch, sitting in a universal class of creation, we are able to see the WHOLE of the Life of the UOR Foundation before it's creation, and begin to define the form and function of the UOR Foundation.

Welcome to the exciting and magical world of quantum, where we define real things before they become real!

\subsection*{The UOR Foundation}
As a WHOLE, the UOR Foundation is the collection of people who believe in the UOR model and the potential in the UOR machine.
We are any human who desires to know what the UOR is and what it can do.
From industry, academia, and government.
We are the people who write the code, test the equipment and services, share better ways to experience the internet and in turn experience your world.
From Individuals and groups
We are the familiar, approachable, and friendly.
From near and far.
We come from all cultures and all ages.
From families and companies.
We are the recluse, odd, and taboo.
From all religions and spiritualities.
We are doers and thinkers.
From the East and the West, the North and the South.
We are a chaotic collection of humans.

\vspace{20pt}
\begin{minipage}{0.95\linewidth}
    \begin{tcolorbox}
    \begin{center}\underline{Who are The UOR Foundation}\end{center}
        \begin{itemize}
            \item \textit{We are a chaotic collection of humans.}
        \end{itemize}
    \end{tcolorbox}
\end{minipage}
\vspace{10pt}


In this chaos, the UOR Foundation \textbf{aims} to provide an open and safe environment for all to explore, study, play and work with the UOR\@.

In this chaos, the UOR Foundation \textbf{vision} to co-create a human-friendly environment that allows for the care and feeding for the core UOR Concept and Machine\footnote{The ``UOR machine'' is a physical, real, unique operating computer. The ``UOR'' is a theory or model proven by the fact that the UOR Machine works and is real. We view ``UOR'' as the theory or framework. A ``UOR Machine'', or ``UOR Object'', etc., is an applied instance of that theory.} source code.


\vspace{20pt}
\begin{minipage}{0.95\linewidth}
    \begin{tcolorbox}
    \begin{center}\underline{Vision \& Aim of the UOR Foundation}\end{center}
        \begin{description}
            \item[Aim:] To \textit{provide} an open and safe environment for all peoples to explore, study, play and work with the UOR\@. 
            \item[Vision:] To \textit{co-create} a human-friendly environment that allows for the care and feeding of the core UOR Concept and UOR Object. 
        \end{description}
    \end{tcolorbox}
\end{minipage}
\vspace{10pt}

\subsection*{The UOR Machine}
As a WHOLE, The UOR Machine is a bridge or tool that looks into a very large, very powerful, omnipresent, complex system called the Internet.
The \textit{UOR Machine} gives us a ``lens'' to peek inside the Internet and observe it as a quantum, complex system.

It also runs a runtime environment for the user, that can reference any data, task, or service found inside the Internet.
This \textit{runtime environment} is an window that allows users to access and manipulate parts and components of the vast complex system we call the Internet.
In the unknown, UOR's potential is great.

From our view, the WHOLE of the Internet is a quantum system intimately entangled with humans.
Very similar to the economy, one can not simply ``turn off'' the Internet.
Yet, everyone of us access to Internet daily to meet our desires.
This makes the Internet vital to the well-being and happiness for you on a daily basis.
It is our belief that a UOR Machine will elevate the user to a more harmonious and pleasant Internet experience.

The UOR Machine is a serverless, stateless computer running an operating system using a universal or multi-dimensional kernel.
We call it a ``quantum computer''.

For those few who dare to open the hood and see how it works, this might take a bit of faith as we guide you to our UOR island where we discuss the amazing attributes and traits of quantum and multi-dimensional objects and beings.
For the rest of us that just want to take it for a spin, have faith, there is a ``I Believe'' button.
Users and creators, have different roles and responsibilities when operating a UOR Machine, but their aim is always to find harmony and joy when driving a UOR Machine.

To help, let's start with something practical and concrete to ground your thoughts on exactly what is a UOR Machine.
Simply put, the UOR machine is an abundance machine.
That is a machine that creates abundance\ldots
not quite practical or concrete enough?
How about a machine that creates power and strength\ldots
still too abstract?
How about an app that gives you the ability to control the Internet and transform it into you personal computer that is custom tailored to how you want to experience the Internet as it anticipates all your Internet desires.

The potential found in a UOR Machine truly is great.

\subsection*{The U.O.R.}
As a WHOLE, the Universal Object Reference\footnote{Or Referencing. The change in verb tense is more to describe the UOR as a static, concrete thing or a dynamic, operating thing. Both describe exactly what the UOR is and does and can be used interchangeable.} is a framework or model developed by the inventor that guided the creation of the quantum or multi-dimensional computer kernel.
This ``quantum'' kernel powers a specially designed operating system(OS).
Together the kernel and OS make up a UOR Machine.
Or as we like to call it, the ``Quantum Computer''.

From studying the UOR Machine, the theory or framework around the machine is starting to develop.
We simply just call it U.O.R.

The UOR is in it's infancy, and any attempt to clearly define it, fails.
Regardless, the UOR and UOR Machine are intimately connected and compliment each other perfectly.
Due to this, the UOR in \textit{form} of theories, concepts, frameworks, etc\ldots must align with the UOR Machine in \textit{function}.
\subsection*{The WHOLE UOR Foundation}

The WHOLE idea behind the UOR Foundation and the driving force or source of all that the UOR Foundation stands for is twofold.
It includes both the UOR and the UOR Machine.
The theory and the applied.
It is the \textit{purpose} of the UOR Foundation to encourage and inspire it's members to continue the development, evolution, and understanding of both the UOR concept and the UOR Machine, which is an UOR Object.

\vspace{20pt}
\begin{minipage}{0.95\linewidth}
    \begin{tcolorbox}
    \begin{center}\underline{Purpose of the UOR Foundation}\end{center}
        \begin{description}
            \item[Purpose:] to encourage and inspire it's members to continue the development, evolution, and understanding of both the UOR concept and the UOR Object.
        \end{description}
    \end{tcolorbox}
\end{minipage}
\vspace{10pt}


The UOR is a concept and the Machine is a real computer.
Both discovered and created by humans, for humans.
The UOR Foundation always recognizes the human element as the primal and sole being of responsibility for any UOR Machine or Object.
Therefore, the UOR Foundation always places the well-being and benefit of the human over the machine.

\vspace{20pt}
\begin{minipage}{0.95\linewidth}
    \begin{tcolorbox}
    \begin{center}\underline{Principles of the UOR Foundation}\end{center}
        \begin{itemize}
            \item Dedicated to the collection of peoples to provide a safe \& human friendly environment to explore, create, and share\@ UOR objects and concepts. 
            \item Dedicated to study of UOR concepts and objects.
            \item Dedicated to the open development, sustainment, and deployment and open access to the core source code for the UOR Machine\@.
        \end{itemize}
    \end{tcolorbox}
\end{minipage}
\vspace{10pt}

In summary, the WHOLE UOR Foundation is a collection of people, dedicated however they can, to provide a human friendly environment to explore, create, and share\@ UOR objects and concepts; to study UOR\@; and to develop, sustain, and deploy the core source code for the UOR Machine\@.

\section*{What is a Part?}
\subsection*{Dividing an Ecosystem of Great Complexity}
Obviously, the first split or divide of a whole gives you two parts or components of the whole.
When you divide an idea, like the UOR Foundation, it is a conceptual division.
A meta-physical division, not a physical divide.

The UOR Foundation split the first two parts or components after the \textit{first divide} into two classes for all parts \& components of the whole UOR Foundation.
A class of \textbf{Governance}.
And a class of \textbf{Evolution}.

\subsection*{The Core Primary Parts}
After the 1\textsuperscript{st} divide, we are left with two meta-physical or conceptual fundamental, core parts or components of the UOR Foundation:
    \begin{itemize}
        \item \textbf{Evolution} 
        \item \textbf{Governance}
    \end{itemize}

Every part or component, to include the two primary components of governance and evolution, that operates and exists in relation to the UOR Foundation will always fall under the \underline{authority} \& \underline{responsibility} of one and only one primary class.

It is the responsibility of the Foundation to further develop and create more refined and defined roles \& responsibilities.
It is recommended to take an approach of using the three levels of truth for any single WHOLE truth.
These levels are the Universal, Local, and Unique.

\subsection*{The 3 Levels of Truth}
As an example, the future financial department of the UOR Foundation will have a very specific, \textbf{unique} job or task to provide monthly financial reports to the members of the Foundation.

Those reports are created, sorted and published within a \textbf{local} set of policies and instructions created out of the vast financial knowledge and history of non-profit organizations and old-fashion bookkeeping.
Interestingly, while unique tasks are operating under a local truth, there are many unique tasks and jobs operating unbeknownst to the unique monthly financial reports task.

Now we all know no really reads these reports except organizational leaders and Wallstreet.
But for those souls who truly live or die based decisions greatly influenced by these reports, the people making those decisions operate at a \textbf{universal} truth to that organization.
It behooves all to elect and retain members that understand universally independently both the Governance and Evolution components as well as the dynamic and chaotic relationships between the two.

It is up to each organization or organism to recognize and define the unique, local, and universal policies and instructions to ensure the most profitable products and services are provided for the members, community, and others regardless of the state the whole organization.

\subsection*{Greatness}
Great acts are done as we walk gently on the shoulders of giants.
We would like to remind the reader that the UOR is a journey into the unknown.
The Foundation embraces quantum or multi-dimensional systems, and understands that all areas of study and work influence the UOR machine.
Under such a unimaginable knowledge space of human experience and history, we would be foolish to think mistakes will not be made.

In order to always maintain the first principle of the UOR Foundation to provide a \textit{safe \& human friendly environment}, mistakes are not only accepted, but encouraged to be shared.
With the potential for a very large pool of individuals, across the globe, there will inevitably be challenges to individual core beliefs and values.
We only remind you that patience \& gentleness is needed to see the diamond in the rough.
\footnote{When a dog eats the diamond ring, it takes patience and hopefully only few close inspections of dog shit to find the ring.}

We bring this up here, because after the first divide authorities and responsibilities must be assigned to members.
Creating an illusion of hierarchy.
By recognizing that this hierarchy empowers humans over other humans, we can overcome or buttress our fears by simply stating that all levels of truth are a whole truth when taken together.

No one truth or level of truth has a monopoly or authority over another.
In fact, all parts or components of the UOR Foundation, operate within one of the two sources of responsibility \& authority:
Governance or Evolution.

As the UOR Foundation grows and evolves from an idea into a large, robust, open community, we believe all activities of it's members can fall under one of the two primary classes.
The activities of each member vary and can cross-over from the two classes.
To remain in harmony with the Foundation's core principles, \textit{to provide a safe \& human friendly environment}, individual members can perform acts under both classes.
The ``acts'' that influence the Foundation's human friendly environment, advance the study of the UOR, and evolve the core source code are just as vast and complex as the individual or group acting.

\section*{Parts of Parts}
\subsection*{Governance and Evolution}
The first organizational division of the UOR Foundation separates all actions and potential acts into two distinct components: \textbf{Governance} and \textbf{Evolution}.
Together, these components embody the duality of \textit{form} and \textit{function}, each playing a critical role in achieving a stable, friendly, creative environment.

The Governance \& Evolution model proposed is a set of principles, responsibilities and symbolism unique to that component.
This group of policy and members create the \textit{local} data-set of co-ordination and instructions specific to that component.
It is the \underline{responsibility} of other components to be fully aware of the actions and potential actions of the other components.
Here the core Principles are used as the bridge to co-ordinate and co-create between all components to align with the Foundation's vision and purpose.

\subsection*{Governance (Form)}
Governance represents the static, absolute \textit{form} of the Foundation.
The written and followed policy and instructions that co-ordinate the tasks and jobs within the Governance component of the Foundation.
It makes up the form or structure of the entire Foundation.
Allowing a place and purpose for any member.

It provides the structural integrity and stability required to support dynamic innovation.
Governance embodies \textit{stewardship}, aimed at supporting the Foundation's principles and vision.

\vspace{20pt}
\begin{minipage}{0.95\linewidth}
    \begin{tcolorbox}
        \begin{center}\underline{Core Governance Principles}\end{center}
        \begin{itemize}
            \item \textbf{Integrity:} All actions align with the foundation's vision and principles.
            \item \textbf{Transparency:} Processes are open and accessible to foster trust.
            \item \textbf{Strength:} Resilient in a stable and absolute framework for the organization.
            \item \textbf{Honesty:} Openness to Unify diverse perspectives under a shared purpose.
            \item \textbf{Positivity:} Decisions are guided by constructive and forward-looking intentions.
        \end{itemize}

        \begin{center}\underline{Governance Responsibilities}\end{center}
        \begin{itemize}
            \item Attracting and retaining \textit{Global Talent}.
            \item Develop and administer the Governance \textit{Authorities \& Responsibilities}.
            \item Manage and develop the \textit{Organization Structure}.
            \item Ensuring the integrity of the \textit{Core-Source-Code}.
            \item Co-ordinate and align Governance principles with Core principles.
        \end{itemize}

        \begin{center}\underline{Governance Symbolism}\end{center}
        \begin{itemize}
            \item \textbf{A Tree:} The trunk and roots, supporting growth and stability.
            \item \textbf{A Mirror:} Reflecting clarity, honesty, and truth.
        \end{itemize}
    \end{tcolorbox}
\end{minipage}

\subsection*{Evolution (Function)}
Evolution represents the dynamic, changing \textit{function} of the UOR Foundation.
The written and followed policy and instructions that co-ordinate the tasks and jobs within the Evolution component.
Making up the function or flow of UOR objects and concepts.
Evolution allows any member to define their function with purpose in the Foundation.

It embodies \textit{innovation}, driving creativity and challenging existing structures within the safe boundaries set by Governance.
Providing the channels and protocols to support creative collaboration.
The policy and instructions defined by Governance shall be designed with the desires and intentions that allow the sovereignty of Evolution to act without judgement or punishment from Governance.

\vspace{20pt}
\begin{minipage}{0.95\linewidth}
    \begin{tcolorbox}
        \begin{center}\underline{Core Evolution Principles}\end{center}
        \begin{itemize}
            \item \textbf{Creativity:} Freedom to experiment and iterate.
            \item \textbf{Free-Thinking:} Embracing diverse ideas without judgment.
            \item \textbf{Inclusiveness:} Valuing all contributors, regardless of background and origin.
            \item \textbf{Positive Reinforcement:} Encouraging and celebrating contributions.
            \item \textbf{Non-Judgment:} Shared errors and failures are allowed and encouraged.
        \end{itemize}


        \begin{center}\underline{Core Evolution Responsibilities}\end{center}
        \begin{itemize}
            \item Provide a safe, inclusive space for experimentation.
            \item Develop and administer the Evolution Roles \& Responsibilities
            \item Testing and challenge the policies and core-source-code.
            \item Encouraging community collaboration and engagement.
            \item Developing and refining new bundles and solutions.
            \item Adapting to external demands and technological advances.
        \end{itemize}

        \begin{center}\underline{Core Symbolism}\end{center}
        \begin{itemize}
            \item \textbf{Forest Creatures:} Reveal new and promising paths.
            \item \textbf{A Candle:} Lights new paths.
        \end{itemize}
    \end{tcolorbox}
\end{minipage}
\section*{Bridging the First Divide}
Together, both the Evolution and Governance components provide the function and form of the UOR Foundation as a WHOLE\@.
Independently, each component has it's own self form and function that define or co-ordinate all jobs and tasks within the respective component.
It is the mission of each component to administrate the jobs and tasks to members of the Foundation.
To guide and assists members in completing assigned jobs and tasks by providing the necessary tools and safe environment.

Evolution generates and maintains the job and task list for the UOR Machine.
Governance generates and maintains the job and task list for Humans.

Each component operates independently and with full-awareness and trust of the other.
Trust is paramount, if not critical, for success.
With clear Roles \& Responsibilities, each component and it's assigned members can rely on other parts for what they need.
Allowing each member to focus on the desired Job \& Task at hand.
It would be foolish to say that this trust will never be challenged.

It is this tension in trust that will drive greater collaboration or drive us apart.
The interplay or tension between the two is the driving force behind the success of the Foundation regardless of it's whole state.
Therefore, a special Role is required.

\subsection*{A Special Part}
The ingenious method deployed by the UOR Machine is that the Machine is treated and seen just as any other agnostic object on the internet.
In other words, the UOR Machine computes itself as any other data, task, or service found on the internet.
It can and does treat itself, the UOR Machine, as some agnostic data, task, or service.
To distinguish itself from the rest of the internet, it's key:value or hash is treated special.
This unique, special value is known to only to itself and not other as \textbf{self}.

\vspace{20pt}
\begin{minipage}{0.95\linewidth}
    \begin{tcolorbox}
        \begin{center}\underline{A Universal Computation}\end{center}
        \begin{itemize}
            \item \textit{The UOR Machine computes itself as any other data, task, or service found on the internet.}
        \end{itemize}
    \end{tcolorbox}
\end{minipage}
\vspace{10pt}

Before the 1st divide, the WHOLE exists.
After the divide, there are two parts.
When you combine the two parts, do you have a WHOLE\@?

Not exactly.
You get a perfect copy of the WHOLE\@.
And this is key, it is a \textit{copy} and not the WHOLE\@.

This ``copy'' is a special copy because it is the only perfect copy of itself.
This special case of a part is the \textbf{self}.
Or you can say that this special case is the \textit{self-aware} part of the WHOLE\@.

Due to the special attributes and traits found in the \@.self part, this unique perfect copy is the only \textit{component} that is NOT a part.
Here we finally discern the difference between a component and a part.
All parts are components, but there is only one component that is NOT a part.

\vspace{20pt}
\begin{minipage}{0.95\linewidth}
    \begin{tcolorbox}
        \begin{center}\underline{The Non-Part: The Component}\end{center}
        \begin{itemize}
            \item \textit{All parts are components, but there is only one component that is NOT a part.}
        \end{itemize}
    \end{tcolorbox}
\end{minipage}
\vspace{10pt}

There is only one \@.self component for every WHOLE\@.
Every part of a WHOLE, is also assigned a \@.self component for that part.
In turn, a part literally ``becomes'' a new or other WHOLE\@.

This self.component acts as an excellent discernment between the WHOLE and it's parts.
We find it easier when discuss the WHOLE, to distinguish it's parts as \textit{components}.
When we talk about independent forms and functions of the WHOLE found in other objects, we focus on the \textit{parts} of the WHOLE\@.

\subsection*{The UOR Council}
The importance of the relationship between the two components, Evolution \& Governance, demands it's own special attention.
It is a special component.

The Council combines the Job and Tasks list of both the Evolution \& Governance independent job and task list.

The interplay between Governance and Evolution addresses the natural tension between stability and change.
By design, this model fosters collaboration and innovation while maintaining the integrity of the Foundation.
Together, the two components are the perfect copy of the WHOLE UOR Foundation.

It is critical to address the absolute power and authority that \textit{can} be assigned to a person or group of people over the UOR Foundation.
Anyone one person or group of people with authority over both core components of the Foundation, is a clear concentration of power.
To avoid this, a WHOLE council representing the UOR Foundation as a WHOLE will retain ALL responsibility for ALL act past, present and future within the UOR Foundation.
The WHOLE council will NOT have authority for to act or potentially act for the UOR Foundation or any of it's components and parts.
Each of the two core components, Governance \& Evolution, are the sole authority for the Foundation.

This split in authority and responsibility is designed to elevate pressure from those who act to act freely.
It also concentrates the most important non-acts or decisions about the tension between the two components to the council.
This split can be replicated in each component by creating a council within.
For example, a Governance Council holds the responsibility of the Governance, while other parts or components of the Governance form and function act with authority.

The form and function of a council is worth further development.

\vspace{20pt}
\begin{minipage}{0.95\linewidth}
    \begin{tcolorbox}
        \begin{center}\underline{Principles of ONENESS}\end{center}
        \begin{itemize}
            \item \textbf{Love:} The desire to do good to others.
            \item \textbf{UNITY:} Words and actions of compassion that attract.
            \item \textbf{Integrity:} Absolute trust in another.
        \end{itemize}

        \begin{center}\underline{Responsibilities of ONENESS}\end{center}
        \begin{itemize}
            \item Allow and foster positive change.
            \item Attract and retain unique skills.
            \item Accept the greatness of others.
        \end{itemize}

        \begin{center}\underline{Triad Symbolism}\end{center}
        \begin{itemize}
            \item \textbf{Governance:} The Sequoias, representing stability and strength.
            \item \textbf{Evolution:} The Creatures (Phoenix, Unicorn, etc\ldots), representing renewal and transformation.
        \end{itemize}
    \end{tcolorbox}
\end{minipage}
\vspace{10pt}

A forest representing the Governance.
The creatures representing the Evolution.
The council representing humans.
Together, the three spawn new life and energy.

\subsection*{Councils as a Compass}
A single UOR Foundation Council is needed in the state of Birth-Creation and transition into the Growth states of the Class of Universal Creation.
The Council will work within the following Core Principles to create and unite the two core components.
The Council will always maintain the vision and purpose of the UOR Foundation.
The Components, together and outside the authority of the Council, defines the UOR Foundation Vision, Purpose, and Mission after the Birth-Creation state is complete.
The Council always speaks as ONE voice for the UOR Foundation.

For example, Governance and Evolution components or departments, work together to amend the Foundations Mission statement.
The Council is does not create the new statement and only guides or assists the components in the view and perspective of the Council.
After full acceptance between the two components or departments, the UOR Council announces as a single voice the new mission of the Foundation.

This model of full acceptance between the two core components can control the voice or actions of the council is critical in separating a concentration of power.
Together the special components of Governance, the WHOLE Council, and Evolution make up the core triad that make up the WHOLE UOR Foundation.
This triad holds absolute Authority \& Responsibility for the UOR Concept \& Objects.

Together, the triad acts as the compass to guide and direct the UOR Foundation into the unknown.

\section*{In Closing}
Isaac Newton found truth in simplicity; a single unit or WHOLE is a great ecosystem of complexity.
By simple splits and not the multiplication of things, do we slowly reveal the truth.
Recognizing this, it is up to us to discern what is WHOLE and what is not.

The first divide created two parts.
The relationship between the two created a third component.
The Triad is the two parts and one component, it is a perfect copy of the WHOLE\@.

Addressing head-on the real and perceived threats and fears of the concentration of power, we clearly split authority \& responsibility between the Parts \& Component. 
We recognize the tension this creates and look forward to the interesting solutions proposed by the activities spawned by the relationships between \textit{all} the components of the WHOLE UOR Foundation.

In closing, we leave you with a new thought\ldots
We hiked into a quantum forest and stand in awe and amazement of what we are experiencing.
The future is bright in this forest.
Come on in, we can't wait to show you the magical and magnificent creatures we found.
\vspace{10pt}

% Customize epigraph
\setlength{\epigraphwidth}{0.95\textwidth} % Adjust epigraph width
\renewcommand{\textflush}{flushleft}     % Align quote to the left
\renewcommand{\sourceflush}{flushright}  % Align author to the right
\renewcommand{\epigraphsize}{\itshape} % Font size and style for quote


\emph{Love, UNITY and Integrity}{--- Core Principles of ONENESS}

\end{document}

